### 2020-09-23 manuscript/manuscript.rmd
add GTR_CAT60 results

Due to computational limitations of GTR models, we only ran GTR+CAT and GTR+nCAT60 models on representative matrices with Choanimalia sampling. We found that for both Whelan2017 and Philippe2009 matrices, support shifted from Porifera-sister with Poisson+CAT model to Ctenophora-sister using GTR+CAT model. Moreover, we also found all results strongly supported Ctenophora-sister with GTR+nCAT60 models.

@@

>>>>

Due to computational limitations of GTR models, we only ran GTR+CAT and GTR+nCAT60 models on representative matrices with Choanimalia sampling. We found that for Whelan2017 matrices, support shifted from Porifera-sister with Poisson+CAT model to Ctenophora-sister using GTR+CAT model. Moreover, we also found all results strongly supported Ctenophora-sister with GTR+nCAT60 models.

@@

branch_lengths = read.csv("../data_processed/tables/branch_lengths.tsv", header=TRUE, sep="\t")

branch_lengths$Clade =
    factor(
        branch_lengths$Clade,
        levels = c("Bilateria", "Cnidaria", "Placozoa", "Porifera", "Ctenophora", "Choanoflagellata"))

p=ggplot (branch_lengths, aes(x=Clade, y=branch_length, fill=Clade)) + geom_violin(trim=FALSE) + geom_boxplot(width=0.1) + theme_classic()+  labs(x="Clade", y = "Branch Lengths")

p+scale_fill_manual(values=c("#E6BEFF", "#911EB4", "#82D1F4", "#009E73", "#E69F00", "#4363D8"))

Bilateria_branch_mean = branch_lengths %>% filter(Clade=="Bilateria") %>% summarise(mean = mean(branch_length), n = n())
Porifera_branch_mean = branch_lengths %>% filter(Clade=="Porifera") %>% summarise(mean = mean(branch_length), n = n())
Ctenophora_branch_mean = branch_lengths %>% filter(Clade=="Ctenophora") %>% summarise(mean = mean(branch_length), n = n())

taxa_map=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Whelan2017/strict.phy")
outgroup= taxa_map %>% filter (clade_assignment=="Choanoflagellida")
Bilateria= taxa_map %>% filter (clade_assignment=="Bilateria")
Cnidaria= taxa_map %>% filter (clade_assignment=="Cnidaria")
Placozoa= taxa_map %>% filter (clade_assignment=="Placozoa")
Porifera= taxa_map %>% filter (clade_assignment=="Porifera")
Ctenophora= taxa_map %>% filter (clade_assignment=="Ctenophora")

tree1= read.tree("../trees_new/iqtree/Whelan2017_strict.model_test.treefile")
tree1_rooted =  root(tree1, outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree1_rooted) +
  geom_cladelabel(node=90, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=114, label="Porifera", color="#009E73") +
  geom_hilight(node=90, fill="#E69F00") +
  geom_hilight(node=114, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 95)) + ggtitle("    WAG+C60")

tree2=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT60.con.tre")
tree2_rooted =  root(tree2, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree2_rooted) +
  geom_cladelabel(node=119, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=100, label="Porifera", color="#009E73") +
  geom_hilight(node=119, fill="#E69F00") +
  geom_hilight(node=100, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1)) + ggtitle("    Poisson+nCAT60")

tree3=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT90.con.tre")
tree3_rooted =  root(tree3, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree3_rooted) +
  geom_cladelabel(node=100, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=130, label="Porifera", color="#009E73") +
  geom_hilight(node=100, fill="#E69F00") +
  geom_hilight(node=130, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1)) + ggtitle("    Poisson+nCAT90")
p3 = flip(p3, 100, 98)

tree4=read.tree("../trees_new/phylobayes/Whelan2017_strict.bpcomp.con.tre")
tree4_rooted =  root(tree4, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree4_rooted) +
  geom_cladelabel(node=100, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=130, label="Porifera", color="#009E73") +
  geom_hilight(node=100, fill="#E69F00") +
  geom_hilight(node=130, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) <1)) + ggtitle("    Poisson+CAT")
p4 = flip(p4, 100, 98)

tree5=read.tree("../trees_new/phylobayes/Whelan2017_strict.phy_GTR_CAT.con.tre")
tree5_rooted =  root(tree5, outgroup$relabelled_name, resolved.root=TRUE)
p5=ggtree(tree5_rooted) +
  geom_cladelabel(node=119, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=100, label="Porifera", color="#009E73") +
  geom_hilight(node=119, fill="#E69F00") +
  geom_hilight(node=100, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1)) + ggtitle("    GTR+CAT")

ggarrange(p1, p2, p3, p4, p5,  ncol  = 3, nrow = 2, labels = c("A", "B", "C", "D" , "E"), common.legend = TRUE)

taxa_map=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Philippe2009/Philippe2009.nex")
outgroup= taxa_map %>% filter (clade_assignment=="Choanoflagellida")

tree1= read.tree("../trees_new/iqtree/Philippe2009_only_choanozoa.WAG+C60.treefile")
tree1_rooted =  root(tree1, outgroup=outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree1_rooted) +
  geom_cladelabel(node=85, label="Ctenophora") +
  geom_cladelabel(node=76, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=33, label="Placozoa") +
  geom_cladelabel(node=53, label="Bilateria") +
  geom_cladelabel(node=51, label="Cnidaria") +
  geom_hilight(node=85, fill="#E69F00") +
  geom_hilight(node=76, fill="#009E73") +
  geom_hilight(node=33, fill="#82D1F4") +
  geom_hilight(node=53, fill="#E6BEFF") +
  geom_hilight(node=51, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 95), hjust=-.3, size=2) + ggtitle("    WAG+C60")

tree2=read.tree("../trees_new/sensitive/Philippe2009_only_choanozoa.phy_Poisson_CAT60.con.tre")
tree2_rooted =  root(tree2, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree2_rooted) +
  geom_cladelabel(node=83, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=32, label="Placozoa") +
  geom_cladelabel(node=58, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=83, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=32, fill="#82D1F4") +
  geom_hilight(node=58, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT60")

tree3=read.tree("../trees_new/sensitive/Philippe2009_only_choanozoa.phy_Poisson_CAT150.con.tre")
tree3_rooted =  root(tree3, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree3_rooted) +
  geom_cladelabel(node=83, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=32, label="Placozoa") +
  geom_cladelabel(node=58, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=83, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=32, fill="#82D1F4") +
  geom_hilight(node=58, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT90")

tree4=read.tree("../trees_new/phylobayes/Philippe2009_only_choanozoa.bpcomp.con.tre")
tree4_rooted =  root(tree4, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree4_rooted) +
  geom_cladelabel(node=58, label="Ctenophora") +
  geom_cladelabel(node=84, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=35, label="Placozoa") +
  geom_cladelabel(node=60, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=58, fill="#E69F00") +
  geom_hilight(node=84, fill="#009E73") +
  geom_hilight(node=35, fill="#82D1F4") +
  geom_hilight(node=60, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+CAT")

tree5=read.tree("../trees_new/phylobayes/Philippe2009_only_choanozoa.phy_GTR_CAT.con.tre")
tree5_rooted =  root(tree5, outgroup$relabelled_name, resolved.root=TRUE)
p5=ggtree(tree5_rooted) +
  geom_cladelabel(node=58, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=38, label="Placozoa") +
  geom_cladelabel(node=61, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=58, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=38, fill="#82D1F4") +
  geom_hilight(node=61, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    GTR+CAT")
p5 = flip(p5, 85, 38)

ggarrange(p1, p2, p3, p4, p5,  ncol  = 3, nrow = 2, labels = c("A", "B", "C", "D" , "E"), common.legend = TRUE)
